---
title       : Gross Debt - Leaflet Choropleth
subtitle    : Shiny Application
author      : Sandra Meneses
job         : Student
framework   : io2012        # {io2012, html5slides, shower, dzslides, ...}
highlighter : highlight.js  # {highlight.js, prettify, highlight}
hitheme     : tomorrow      # 
widgets     : []            # {mathjax, quiz, bootstrap}
mode        : selfcontained # {standalone, draft}
knit        : slidify::knit2slides
---

## Synopsis

A Choroplet map is printed using data from the eurostat throgh the package of the same name.
In this case the "General government gross debt - annual data" with code "teina225" was chosen. 
The Shiny application let us select the year and the units, then, the app will show the map colared per the criteria and show the data as a table in a second panel.


```{r message=FALSE, warning=FALSE, echo=FALSE}
library(knitr)
library(dplyr)
library(leaflet)
library(eurostat)
opts_chunk$set(echo = TRUE, warning = FALSE,message=FALSE)
```

## Data

The data is download from the eurostat using the function get_eurostat.
Source of Data: [Eurostat General government gross debt - annual data](http://ec.europa.eu/eurostat/tgm/table.do?tab=table&plugin=1&language=en&pcode=teina225)

```{r}
gross_debt <- get_eurostat("teina225", time_format = "num")
kable(gross_debt[1:3,])
```

---

## Data transforming

To print the map the data with year 2015 and the unit "PC_GDP: Porcentage of gross domestic product (GDP)" is filtered.
The function **merge_eurostat_geodata** merges the dataset with geospatial data as shown in the next example.

```{r}
year= 2015
uni = "PC_GDP"
gross_debt_year <- gross_debt %>% filter(time == year & unit == uni)
# merge the filter data with wgeospatial data 
gross_debt_geo <- merge_eurostat_geodata(gross_debt_year, geocolumn="geo", resolution=60,
     	                    output_class="spdf", all_regions=FALSE)
kable(gross_debt_year[1:2,])
```

---
## Map

The geospatial data is displayed using the leaflet package as shown in code example. 

```{r cache=TRUE}
pal <- colorBin("Spectral", gross_debt_geo$values, pretty = TRUE)
country_popup <- paste0(as.character(gross_debt_geo[["NUTS_ID"]])," ", gross_debt_geo[["values"]])
map = leaflet(data = gross_debt_geo) %>% addTiles() %>% setView(10,55,zoom = 3) %>%
  addPolygons(fillColor = ~pal(values), stroke = FALSE,
              popup = country_popup)%>%
  addLegend("bottomright", pal = pal, values = ~values,
            title = paste0(uni," ",year))
```

---

## Shiny App

Shiny is a web application framework for R which let us turn our analyses into interactive web applications without knowledge of HTML, CSS, or JavaScript.

The Shiny App was built based on [this example.](http://shiny.rstudio.com/gallery/superzip-example.html)

You can find the final application in this [link](https://symeneses.shinyapps.io/gross_debt_-_eurostat/).


